---
title: "example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(PARIS)
```

library(ggrepel)
library(openxlsx)

select_pairs("/mnt/data/DepMap19Q3/Models_DDR_vs_DDR/x_paper/", coeff.filter = T) -> mydata_DDR
select_pairs("/mnt/data/DepMap19Q3/Models_DDR_vs_ALL/x_paper/", coeff.filter = T) -> mydata_ALL

#write files
file_selected_pairs_DDR <- "/mnt/data/DepMap19Q3/Models_DDR_vs_DDR/x_paper/Selected_genes_DDR_vs_DDR.xlsx"
wb <- createWorkbook()
addWorksheet(wb, "er")
addWorksheet(wb, "eg")
addWorksheet(wb, "ec")
addWorksheet(wb, "mr")
addWorksheet(wb, "mg")
addWorksheet(wb, "mc")

writeData(wb, "er", filter(mydata_DDR, group == "er"), startRow = 1, startCol = 1)
writeData(wb, "eg", filter(mydata_DDR, group == "eg"), startRow = 1, startCol = 1)
writeData(wb, "ec", filter(mydata_DDR, group == "ec"), startRow = 1, startCol = 1)
writeData(wb, "mr", filter(mydata_DDR, group == "mr"), startRow = 1, startCol = 1)
writeData(wb, "mg", filter(mydata_DDR, group == "mg"), startRow = 1, startCol = 1)
writeData(wb, "mc", filter(mydata_DDR, group == "mc"), startRow = 1, startCol = 1)

saveWorkbook(wb, file = file_selected_pairs_DDR)

file_selected_pairs_ALL <- "/mnt/data/DepMap19Q3/Models_DDR_vs_ALL/x_paper/Selected_genes_DDR_vs_ALL.xlsx"
wb <- createWorkbook()
addWorksheet(wb, "er")
addWorksheet(wb, "eg")
addWorksheet(wb, "ec")
addWorksheet(wb, "mr")
addWorksheet(wb, "mg")
addWorksheet(wb, "mc")

writeData(wb, "er", filter(mydata_ALL, group == "er"), startRow = 1, startCol = 1)
writeData(wb, "eg", filter(mydata_ALL, group == "eg"), startRow = 1, startCol = 1)
writeData(wb, "ec", filter(mydata_ALL, group == "ec"), startRow = 1, startCol = 1)
writeData(wb, "mr", filter(mydata_ALL, group == "mr"), startRow = 1, startCol = 1)
writeData(wb, "mg", filter(mydata_ALL, group == "mg"), startRow = 1, startCol = 1)
writeData(wb, "mc", filter(mydata_ALL, group == "mc"), startRow = 1, startCol = 1)

saveWorkbook(wb, file = file_selected_pairs_ALL)


##ANALYSIS STRINGDB
#subset by threshold
mydata_DDR_sub <- subset_by_threshold(mydata_DDR, "e", 0.4)
#retrieve stringdb interaction
mydata_DDR_sub_string <- get_stringdb_interactions(mydata_DDR_sub)
mydata_DDR_sub_string_freq <- compute_interaction_freq(mydata_DDR_sub, mydata_DDR_sub_string)
#plot combined score
plot.stringdb.interactions.combined.score.by.group(mydata_DDR_sub_string)
#plot freq of interaction in selected pairs by group
plot.stringdb.interactions.by.group(mydata_DDR_sub_string_freq)

#compare DDR vs DDR and DDR vs ALL commonly by group
inner_join(mydata_DDR, mydata_ALL, by = c("gene", "c", "group")) %>%
  ggplot(aes(scaled.x, scaled.y))+geom_point()+
  facet_wrap(~group)+geom_smooth(method = "lm")+
  stat_cor()+
  xlab("scaled importance DDR vs DDR")+ylab("scaled importance DDR vs ALL")+theme_bw()+
  theme(text = element_text(size = 20), axis.text = element_text(colour = "black"))+
  geom_label_repel(data = . %>% mutate(labels=ifelse((scaled.x > 0.4 | scaled.y > 0.4), as.character(interaction(gene,c)), "")), aes(label=labels), box.padding = 1)


#PARALOGS ANALYSIS
paralogsDDR <- get_paralog_biomart(unique(c(mydata_DDR$gene))) %>% as_tibble() %>% filter(hsapiens_paralog_associated_gene_name != "")
colnames(paralogsDDR) <- c("gene", "c")
paralogsDDR$paralogs <- TRUE

left_join(mydata_DDR, paralogsDDR) %>% replace_na(list(paralogs = "FALSE")) %>%
  ggplot(aes(paralogs, scaled))+
  geom_boxplot(outlier.shape = NA)+facet_wrap(~group)+geom_jitter(width = 0.2)+stat_compare_means()+
  theme_bw()+
  theme(text = element_text(size = 20), axis.text = element_text(colour = "black"))+
  ylab("scaled importance score")

left_join(mydata_ALL, paralogsDDR) %>% replace_na(list(paralogs = "FALSE")) %>%
  ggplot(aes(paralogs, scaled))+
  geom_boxplot(outlier.shape = NA)+facet_wrap(~group)+geom_jitter(width = 0.2)+stat_compare_means()+
  theme_bw()+
  theme(text = element_text(size = 20), axis.text = element_text(colour = "black"))+
  ylab("scaled importance score")
